draft_group-6

### 2025-12-06 draft_group-6.Rmd
final finished updated draft

We also carried out:
- Feature selection using stepwise regression and subset selection for logistic regression
- Regularization techniques (ridge/lasso) when appropriate
- Dimensionality reduction (e.g., PCA) if needed to improve KNN performance
- Hyperparameter tuning for KNN (choice of k), QDA (regularization), and boosting (learning rate, number of trees)

>>>>

We also carried out:
- Feature selection using stepwise regression and subset selection for logistic regression
- Regularization techniques (ridge/lasso) when appropriate
- Dimensionality reduction (e.g., PCA) if needed to improve KNN performance
- Hyperparameter tuning for KNN (choice of k)
